### 2016-06-22 Paper_v1.tex
Jun22

@@

%The ensemble of models captured the dynamic distribution of metabolic flux.
%The ensemble of dynamic models predicted that most of the carbon flux going through glycolysis and the TCA cycle,
%while the constraint based approach predicted most of the carbon flux went through the Entner-Doudoroff pathway and only part of glycolysis.
% We present the first dynamic, cell-free model of \textit{E. coli} metabolism and biosynthesis at this scope.
% While the early models of Shuler and coworkers achieved large-scale, dynamic descriptions of single cells \citep{1984_domach_shuler_BiotechBioeng_01}, and the stoichiometric models associated with the FBA approach are computationally efficient amd widespread \citep{2009_feist_palsson_NatRevMicrobio}, none have yet been able to construct genome-scale kinetic models of cell-free \textit{E. coli} metabolism.
% This study should provide a foundation for genome-scale, dynamic modeling of cell-free \textit{E. coli} metabolism, toward industrial-scale biosynthetic production.
%However, the low sensitivities to glucose and oxygen only apply in the specific case of the parameter sets that were studied.
%When other species' initial conditions and associated parameters are different, glucose and oxygen could become more important to CAT production.

@@

>>>>

\subsection*{Sensitivity analysis on FBA system}
We conducted global sensitivity on certain fluxes' upper bounds within a constraint-based FBA system, with protein export rate as the objective function.

@@

%The ensemble of models captured the dynamic distribution of metabolic flux.
%The ensemble of dynamic models predicted that most of the carbon flux going through glycolysis and the TCA cycle,
%while the constraint-based approach predicted most of the carbon flux went through the Entner-Doudoroff pathway and only part of glycolysis.
% We present the first dynamic, cell-free model of \textit{E. coli} metabolism and biosynthesis at this scope.
% While the early models of Shuler and coworkers achieved large-scale, dynamic descriptions of single cells \citep{1984_domach_shuler_BiotechBioeng_01}, and the stoichiometric models associated with the FBA approach are computationally efficient amd widespread \citep{2009_feist_palsson_NatRevMicrobio}, none have yet been able to construct genome-scale kinetic models of cell-free \textit{E. coli} metabolism.
% This study should provide a foundation for genome-scale, dynamic modeling of cell-free \textit{E. coli} metabolism, toward industrial-scale biosynthetic production.
%However, the low sensitivities to glucose and oxygen only apply in the specific case of the parameter sets that were studied.
%When other species' initial conditions and associated parameters are different, glucose and oxygen could become more important to CAT production.

@@

\begin{figure}[ht]
\centering
\includegraphics[width=1.00\textwidth]{./Figures/AAs_bounded.pdf}
\caption{Total-order global sensitivities of protein export flux to amino acid import flux upper bounds. Each upper bound was varied from 0 to 0.5 mM/hr.}
\label{fig:AAs_bounded}
\end{figure}

\begin{figure}[ht]
\centering
\includegraphics[width=1.00\textwidth]{./Figures/AAs_unbounded.pdf}
\caption{Total-order global sensitivities of protein export flux to amino acid import flux upper bounds. Each upper bound was varied from 0 to 0.5 mM/hr, except the upper bound with respect to which sensitivity was calculated; this was varied from 0 to 10 mM/hr.}
\label{fig:AAs_unbounded}
\end{figure}

\begin{figure}[ht]
\centering
\includegraphics[width=1.00\textwidth]{./Figures/C_Secretion.pdf}
\caption{Total-order global sensitivities of protein export flux to glutamic acid, oxygen and glucose import flux upper bounds, and translation initiation rate upper bound. Lactate, ethanol, acetate, and formate export fluxes were held constant at 0.1 mM/hr in the control case. One of these export fluxes was held constant at 10 mM/hr, while the others were held constant at 0.1 mM/hr, in each of the other four cases.}
\label{fig:C_Secretion.pdf.pdf}
\end{figure}
